### 2015-05-29 writing/SNLI paper/entailment_eval.tex
Optimizations.
Numbers; configs.
Removing transfer section. :P

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop RTE systems
  while sharing components such as common lexical resources and 
  evaluation sets.
% 9 systems compared against
A number of systems have been built using the platform, 9 of them
  applicable to English are publicly distributed with version 1.2.1
  of the software.
% these fall into 2 classes
These fall into two classes of algorithms: 2 are edit distance based,
  whereas the remaining 7 make use of different features in a
  maximum entropy classifier.

%% methodology
%We convert the 3-way classification task in SNLI into the RTE setting
%  by labeling both the \unknown\ and \contradiction\
%  labels as negative entailment, and treating the \entailment\ label as
%  the positive entailment.
%This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run the top performing edit-distance based algorithm and the top
  performing classifier-based algorithm on our test set, as
  determined by performance on the development set.
Note that these models were run using the default configuration
  with minimal tuning.
The results should therefore be taken as a strong baseline for
  RTE-style approaches to the problem, rather than necessarily
  representing the state-of-the-art system's performance on the
  task.
%We run each of the 9 algorithms distributed with EOP on the 2-class
%  SNLI dataset, and report results for the best edit distance 
%  configuration and the best classifier based configuration, as
%  determined by performance on the development set.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{Our corpus}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{67?} & \t{69?} \\	
\t{100d LSTM RNN}            & \t{75?} & \t{76?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{58?} & \t{56?} \\
\t{100d LSTM TreeRNN}            & \t{75?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the our training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}

Note that \todo{something interesting happens}.

>>>>

%
% EOP
%
\paragraph{Excitement Open Platform}
% what is EOP
The Excitement Open Platform is a tool to quickly develop NLI systems
  while sharing components such as common lexical resources and 
  evaluation sets.
% 9 systems compared against
A number of systems have been built using the platform, 9 of them
  applicable to English are publicly distributed with version 1.2.1
  of the software.
% these fall into 2 classes
These fall into two classes of algorithms: 2 are edit distance based,
  whereas the remaining 7 make use of different features in a
  maximum entropy classifier.

%% methodology
%We convert the 3-way classification task in SNLI into the RTE setting
%  by labeling both the \unknown\ and \contradiction\
%  labels as negative entailment, and treating the \entailment\ label as
%  the positive entailment.
%This creates a biased dataset of 66\% negative examples.
% we report the best results from each class
We run the top performing edit-distance based algorithm and the top
  performing classifier-based algorithm on our test set, as
  determined by performance on the development set.
Note that these models were run using the default configuration
  with minimal tuning.
The results should therefore be taken as a strong baseline for
  NLI-style approaches to the problem, rather than necessarily
  representing the state-of-the-art system's performance on the
  task.
%We run each of the 9 algorithms distributed with EOP on the 2-class
%  SNLI dataset, and report results for the best edit distance 
%  configuration and the best classifier based configuration, as
%  determined by performance on the development set.

@@

% The table
\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceS}c@{\hskip \colspaceL}c@{\hskip \colspaceS}c}
\hline
\textbf{System} & \multicolumn{4}{c}{\b{Our corpus}} & \multicolumn{2}{c}{\b{RTE-3}} \\
 & \t{P} & \t{R} & \t{F$_1$} & \t{Acc.} & \t{F$_1$} & \t{Acc.} \\
\hline
\t{Edit Distance} & \t{??.?} & \t{??.?} & \t{??.?} & \t{??.?} & 
                    \t{??.?} & \t{??.?} \\
\t{Classifier}    & \t{67.9} & \t{38.7} & \t{49.3} & \t{7X.X} & 
                    \t{64.2} & \t{65.3} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:eopresults}
3-class accuracy and precision/recall of existing competitive RTE
systems from the Excitement Open Platform.
Results are reported for an edit-distance based algorithm, and a
  classifier-based system.
In order to calibrate the difficulty of the dataset against the 
  classical RTE problems, results are also reported on the (2-class) 
  RTE-3 dataset.
\todo{Cite RTE-3 here.}
\todo{Final numbers}
}
\end{table}
%
% END EOP RESULTS TABLE
%

@@

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d Sum of words}            & \t{79?} & \t{76?} \\
\t{100d RNN}            & \t{75?} & \t{72?} \\	
\t{100d LSTM RNN}            & \t{81.4?} & \t{78.2?} \\
\t{100d TreeRNN}            & \t{69?} & \t{69?} \\
\t{50d TreeRNTN}            & \t{61?} & \t{60?} \\
\t{100d LSTM TreeRNN}            & \t{72?} & \t{73?} \\
\hline
\end{tabular}
\end{center}
% The caption
\caption{
\label{tab:nnresults}
Accuracy in 3-class classification on the our training and test sets for each model.
\todo{Replace with final numbers/dims}
}
\end{table}

\subsubsection{Evaluating on other inference corpora}

To the extent that successfully training a sentence model on our corpus forces that model to encode broadly accurate representations of English scene descriptions, we should expect it to be possible to adapt these representations in a different setting. In this section, we experiment with transfer learning on SICK, the corpus for the most recent NLI shared task.

To perform transfer learning, we take the parameters of strong LSTM RNN model trained on our corpus and use them to initialize new model which trained from that point only on the training portion of SICK. The only newly initialized parameters are the embeddings for words that appear in the new training set, but not in our training set, and those parameters are initialized using GloVe embeddings, as before. We use the same model hyperparameters that were used to train the original model, with the exception of the L2 regularization strength which is re-tuned. We additionally transfer the accumulators that are used by AdaDelta to set the learning rates with the intention of ensuring that the model does not learn too quickly in its first few epochs and destroy the knowledge accumulated in the pre-transfer phase of training.

\begin{table}
\begin{center}
\begin{tabular}{l@{\hskip \colspaceL}@{\hskip \colspaceL}c@{\hskip \colspaceL}c}
\hline
\textbf{Sentence model} & \b{Train}  & \b{Test}\\
\hline
\t{100d LSTM RNN (random init.)}            & \t{100} & \t{71.3} \\
% From: ~/quant/transfer-sick-only-l0.0001-dim50-ed200-td3-pen100-do0.9-0.9-ws1-par0-comp2-cdim1/
\t{100d LSTM RNN (transfer init.)}            & \t{100?} & \t{80?} \\
% From: 
\hline
\end{tabular}
\end{center}

\caption{\label{tab:transferresults}
The performance (\% accuracy) of an LSTM RNN model on SICK under both a random initialization and a transfer initialization copied from a model trained on our corpus.  \todo{Final numbers.}} 
\end{table}

\todo{Why not RTE3?}

We compare the performance of an LSTM model with both the transfer initialization and a normal random initialization. We tune the regularization parameter separately for each case. Table \ref{tab:transferresults} shows these results.

Our transfer model shows the best performance yet reported on SICK for an unaugmented neural network model, and approaches the overall state of the art at 84.6\% \cite{lai2014illinois}, as well as the 84\% level of interannotator agreement, which represents a likely performance ceiling. The randomly initialized model performs relatively poorly. This suggests that the introduction of a large high-quality corpus makes it newly possible to train representation learning models for sentence meaning of a level of quality that is competitive with the best hand-engineered models on inference tasks.
